---
title: "W_UP_01"
author: "Gianna Chevez"
date: "spring 2025"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

It appears that "skill" players have more endurance and thus produce more pushups than the "line" players.

### Numerical Descriptive Results

```{r}
favstats(pushups~position,data=mydata)
```

The mean for the "skill" players have around 50 push ups. The "line" players average is around 17. It is a 33 difference in pushups. The "skill" players have done around 3 times more than the "line" players.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The probability of obtaining this p-value is 0.000009421. Since this value is extremely small, I conclude that "skill" players perform significantly more push-ups than "line" players. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The data shows a significant difference in push-up performance between "skill" and "line" players. On average, "skill" players complete around 50 push-ups, while "line" players average 17, a difference of 33 push-ups. This means "skill" players perform approximately three times more push-ups than "line" players. The extremely small p-value (0.000009421) indicates strong statistical significance, supporting the conclusion that "skill" players have greater endurance and perform significantly more push-ups than "line" players.
